\begin{acknowledgements}
First and foremost, I would like to express my deep and sincere gratitude to my great supervisor Asst. Prof. Dr. Chalermek Intanagontwiwat, for his guidance, patience, and support.
He has advised me for almost seven years since my senior project at the undergraduate level, then, my master thesis, and finally my Ph.D. dissertation. 
He has inspired me in so many ways. I am proud that I was under his supervision.

I greatly appreciate Prof. Dr. Prabhas Chongstitvatana, Prof. Dr. Boonserm Kijsirikul, Assoc. Prof. Dr. Anan Phonphoem, and Asst. Prof. Dr. Kultida Rojviboonchai, for being my dissertation committee and giving several useful comments and suggestions to improve this dissertation. I also acknowledge Rawin Youngnoi, Assoc. Prof. Dr. Paisan Nakmahachalasint, and Asst. Prof. Dr. Manop Wongsaisuwan who gave me a pointer in the mathematical analysis of this dissertation.
 
 I appreciate the CP CU Academic Excellence Scholarship (Ad-cha-ri-ya-kuen-rang Scholarship) from Department of Computer Engineering, Faculty of Engineering, Chulalongkorn University that supports all tuition fee during my Ph.D. program.

 I thank all UbiNET research group members during my Ph.D. program for their discussion and contribution to research works and DMDE research group members for the great time we lived together within the same research room (see the full list at Appendix).

 I am grateful to my family for their endless support and I sincerely thank my dearest Wichearee Thitayarasa who always stands by my side and always understands me.

Last but not least, I would like to thank Department of Computer Engineering for meaningful experience. During my time at this department, I have learned three important lessons:
 \begin{itemize}
 \item \textit{Passion is more important than intelligence.}
 \item \textit{The more we contribute the more we gain.}
 \item \textit{No matter how hard a problem is, if we do not give it up, we will surpass it eventually.}
 \end{itemize}
\end{acknowledgements}
