\chapter{Extended Acknowledgement} 
The regulation limits the front acknowledgement section not to be longer than one page. However, there are so many people  that they deserve to be acknowledged. I would be regret if I cannot express my gratitude to them. Therefore, I use this space acknowledge them.

For UbiNET research group members, I thank Asst. Prof. Dr. Chalermek Intanagontwiwat, Asst. Prof. Dr.  Kultida Rojviboonchai, Tanapoom Danmanee, Kittipat Apicharttrisorn, Jirawat Sirilar, Saran Jenjaturong, Wanchai Ngiwlay, Kulit Na Nakorn, Pongpakdi Taechalertpaisarn, Tossaphol Settawatcharawanit, Kwanjira Narkdej, Phuri Nicro-vanachumrus , Prateep Puttrapornpisut, Vittawus Prueksasri, Chayanin Thaina, Wipawee	Viriyapongsukit, Nattavit Kamoltham, Kiattikun Kawila, Nuttanart Pornprasitsakul, Siam Aurburananont, and Akekanat Saowwapak-adisak. 

For DMDE research group members, I thank Vit Niennattrakul, Haemwaan Sivaraks, Sura Rodpongpun, Pawan Nunthanid, Pongsakorn Ruengronghirunya, Poat Sajjipanon, Angkana Chanrungutai, Thanapong Intharah, Waiyawuth Euachongprasit, Warissara Mee-srikamolkul, Dechawut Wanichsan, and Dararat Srisai.

I thank all my current and past teachers at Chulalongkorn University, Suankularb Wittayalai Nonthaburi School, and Ampornpaisarn School. They have educated me not only for academic matter but also for life. Without them, I would not be here.

I also thank my friends at LarnGear Technology Co., Ltd. including Arnupharp Viratanapanu, Wisit Kunarittipol, and Singhapong Sukuntho.

Last but not least, I thank everyone who always supports and helps me in every aspect in my life. I really appretiate their flowing hearts.

